\documentclass[10pt, a4paper]{article}

\input{cover-letter-themes/theme_selection}

%----------------------------------------------------------------------------------------
%	 THEMES
%----------------------------------------------------------------------------------------

% Define the desired theme out of the following: beige, blue, bw, coral, earth, framed, gray, minimal, onyx, plain
% See screenshots in preview/ directory
\theme{framed}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need a particular field, just remove the content leaving the command, e.g. \jobtitle{}

\name{Laurin Koller} % Your name
\jobtitle{Software Engineer II, AI/ML, Core} % Job title/career
\location{Bärengasse 3, 6317} % Address/location
\phone{+41 079 587 16 59} % Phone number
\mail{laurin.koller@gmail.com} % Mail
\employerinfo{Google Zurich
\\
Europaallee 36 \\
Zurich, 8004 \\
Switzerland } % Contact information of the employer. Make sure to end every row with "\\"

\begin{document}

\makeprofile % Print name & job description

\makecontact % Print defined contact information

\today % Command for inserting today's date.

\letterspace % Command for adding larger vertical space
\makeemployerinfo % Print employer contact information

Dear Hiring Team at Google,

I am excited to apply for a software engineering position at Google. With a Master’s degree in Physics from ETH Zurich and experience in data analysis and large-scale data processing, I am eager to contribute my analytical and programming skills to Google’s innovative projects.

During my Master’s thesis at CERN’s GBAR experiment, I primarily focused on data analysis, using Python to process and interpret experimental data. This involved implementing core machine learning concepts to refine signal detection and analysis. Additionally, I used Apache Spark to process and analyze large datasets efficiently, gaining valuable experience in handling complex data workflows at scale.

Beyond my technical expertise, I am drawn to the international environment of Google and its emphasis on continuous learning. The prospect of working alongside world-class engineers while expanding my knowledge of machine learning and large-scale computing is highly motivating. My experience collaborating with global research teams at CERN has strengthened my adaptability, problem-solving mindset, and ability to work across disciplines.

I would welcome the opportunity to bring my skills and enthusiasm to Google. Thank you for your time and consideration. I look forward to the possibility of discussing how I can contribute to your team.

\letterspace
Sincerely,

\letterspace
Laurin Koller

\end{document}
