\documentclass[10pt, a4paper]{article}

\input{cover-letter-themes/theme_selection}

%----------------------------------------------------------------------------------------
%	 THEMES
%----------------------------------------------------------------------------------------

% Define the desired theme out of the following: beige, blue, bw, coral, earth, framed, gray, minimal, onyx, plain
% See screenshots in preview/ directory
\theme{framed}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------

% If you don't need a particular field, just remove the content leaving the command, e.g. \jobtitle{}

\name{Laurin Koller} % Your name
\jobtitle{Internship in Aircraft Data Analytics} % Job title/career
\location{Bärengasse 3, 6317} % Address/location
\phone{079 587 16 59} % Phone number
\mail{laurin.koller@gmail.com} % Mail
\employerinfo{Federica Lionetto \\
Obstgartenstrasse 25 \\
Kloten, 8302 \\
044 564 00 00 \\
recruiting.services@swiss.com} % Contact information of the employer. Make sure to end every row with "\\"

\begin{document}

\makeprofile % Print name & job description

\makecontact % Print defined contact information

\today % Command for inserting today's date.

\letterspace % Command for adding larger vertical space
\makeemployerinfo % Print employer contact information

Dear Federica Lionetto,

I am excited to apply for the internship in Aircraft Data Analytics at SWISS. With a Master’s degree in physics from ETH Zurich, I have developed a strong foundation in data analysis, programming, and problem solving. I am particularly interested in applying these skills to the real-world challenges in the aviation industry, as well as improving my expertise in machine learning.

During my Master’s thesis at CERN’s GBAR experiment, I worked extensively with data analysis, employing mainly Python and some SQL to process and interpret complex datasets. I also regularly presented my findings to an international collaboration, ensuring that my insights were accessible and applicable to ongoing research. This experience has equipped me with strong analytical and presentation skills, which I am confident will be valuable in this role.

In addition to my programming background, I have a foundational understanding of NLP principles, with some experience training and optimizing different machine learning models, and am proficient in MS Office applications. Although I have not worked extensively with Tableau or cloud providers such as GCP or Azure, I would welcome the opportunity to learn how to use them. My motivation for this internship stems from my keen interest in machine learning and its applications in aviation data analytics. I am excited by the opportunity to develop my skills further in a dynamic and innovative environment.

I would welcome the opportunity to contribute to SWISS and learn from your experienced team. Thank you for considering my application. I look forward to the possibility of discussing how my skills align with the goals of this internship.

\letterspace
Sincerely,

\letterspace
Laurin Koller

\end{document}
